Temporal stability in human interaction networks

### 2017-03-15 paper.tex
arrumado os simbolos < e > no abstract
feita versao do artigo com marcacao das alteracoes

% Use this file as a source of example code for your aip document.
% Use the file aiptemplate.tex as a template for your document.
\documentclass[%
aip,
jmp,%
amsmath,amssymb,
%preprint,%
reprint,%
%author-year,%
%author-numerical,%
]{revtex4-1}
\usepackage{graphicx}% Include figure files
\usepackage{grffile}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines
\usepackage{multirow}
\usepackage{color} % for the notes
\usepackage{etex}
\reserveinserts{58}
%\usepackage{morefloats}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{amsmath}
\hypersetup{
colorlinks,
linkcolor={red!50!black},
citecolor={blue!50!black},
urlcolor={blue!80!black}
}

@@

\begin{abstract}
    This paper reports on stable (or invariant) properties of human interaction networks,
with benchmarks derived from public email lists. Activity, recognized through messages sent,
	along time and topology were observed in snapshots in a timeline, 
and at different scales. Our analysis shows that activity is practically the same for all networks across timescales ranging from seconds to months.
% The most important metrics to the dispersion of participants in the topological measures space are related to centrality (degree, strength and betweenness), followed by symmetry-related metrics and then clustering coefficient.
The principal components of the participants in the topological metrics space remain practically unchanged as different sets of messages are considered.
The activity of participants follows the expected scale-free trace, thus yielding the hub, intermediary and peripheral classes of vertices by comparison against the Erd\"os-R\'enyi model. The relative sizes of these three sectors are essentially the same for all email lists and the same along time. Typically, <15\% of the vertices are hubs, 15-45\% are intermediary and >45\% are peripheral vertices. Similar results for the distribution of participants in the three sectors and for the relative importance of the topological metrics were obtained for 12 additional networks from Facebook, Twitter and Participabr. These properties are consistent with the literature and may be general for human interaction networks, which has important implications for establishing a typology of participants based on quantitative criteria.
\end{abstract}

@@

In this paper we analyze the evolution of human interaction networks.
Directed and weighted representations were built through the observation of replies as links.
Interaction networks from email lists were the most convenient for deriving results and for benchmarking while networks from Facebook, Twitter and Participabr were used for the sake of generalization.
Using a timeline of activity snapshots with a constant number of contiguous messages, we found remarkable stability (or invariance) for important network properties. For instance, activity along different timescales follows specific patterns; the most basic topological metrics can always be combined into characteristic principal components; and the fractions of participants in different sectors do not vary with time. This is not an intuitive result, given that participants constantly transition in network structure. Because these properties were shared by networks from various sources, and are consistent with the literature in complex networks~\cite{newmanBook}, we advocate that the conclusions might be valid for general classes of interaction networks. In particular, this allows us to 
bridge the gap between data analysis and social sciences in the discussion of types of networks and of participants.
It is worth noting that typologies are the canon of scientific literature for the classification of human agents, with pragmatic standards~\cite{myers} and critical paradigms~\cite{adorno,typCanon}.

@@

@@

\begin{table}
\centering
\caption{Columns $date_1$ and $date_M$ have dates of first and last messages from the 20,000 messages considered in each email list.
$N$ is the number of participants (number of different email addresses),
$\Gamma$ is the number of discussion threads (count of messages without antecedent),
$\overline{M}$ is the number of messages missing in the 20,000 collection
($100\frac{23}{20000}=0.115$ percent in the worst case).
}
\label{tab:genLists}
\begin{tabular}{|l|c|c|c|c|c|}\hline
list & $date_1$ & $date_{M}$    & $N$  & $\Gamma$ & $\overline{M}$ \\\hline
\input{tables/tab1Overview}
\end{tabular}
\end{table}
The data and scripts used to derive the results, figures and tables, and this article itself are publicly available. Email messages are downloadable from the Gmane public database~\cite{Gmanewikipedia}.
Data annotated from Facebook and Twitter are in a public repository~\cite{fbtwData}.
Data from Participabr were used from the linked data/semantic web RDF triples~\cite{opa}, available in~\cite{datahub}.
Computer scripts are delivered through a public domain Python PyPI package and an open Git repository~\cite{gmanePack}.
This open approach to both data and scripts reinforces the scientific aspect of the contribution~\cite{openSci} and mitigates ethical and moral issues involved in researching systems constituted of human individuals~\cite{anPhy,ccs15}.

>>>>

% Use this file as a source of example code for your aip document.
% Use the file aiptemplate.tex as a template for your document.
\documentclass[%
aip,
jmp,%
amsmath,amssymb,
%preprint,%
reprint,%
%author-year,%
%author-numerical,%
]{revtex4-1}
\usepackage{graphicx}% Include figure files
\usepackage{grffile}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines
\usepackage{multirow}
\usepackage{color} % for the notes
\usepackage{etex}
\reserveinserts{58}
%\usepackage{morefloats}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{soul}
\hypersetup{
colorlinks,
linkcolor={red!50!black},
citecolor={blue!50!black},
urlcolor={blue!80!black}
}

@@

\begin{abstract}
    This paper reports on stable (or invariant) properties of human interaction networks,
	with benchmarks derived from public email lists. Activity\hl{, recognized through messages sent,}
	along time and topology were observed in snapshots in a timeline, 
and at different scales. Our analysis shows that activity is practically the same for all networks across timescales ranging from seconds to months.
% The most important metrics to the dispersion of participants in the topological measures space are related to centrality (degree, strength and betweenness), followed by symmetry-related metrics and then clustering coefficient.
The principal components of the participants in the topological metrics space remain practically unchanged as different sets of messages are considered.
The activity of participants follows the expected scale-free trace, thus yielding the hub, intermediary and peripheral classes of vertices by comparison against the Erd\"os-R\'enyi model. The relative sizes of these three sectors are essentially the same for all email lists and the same along time.
	Typically, \hl{$<15\%$ of the vertices are hubs, 15-45\% are intermediary and $>45\%$ are peripheral vertices}. Similar results for the distribution of participants in the three sectors and for the relative importance of the topological metrics were obtained for 12 additional networks from Facebook, Twitter and Participabr. These properties are consistent with the literature and may be general for human interaction networks, which has important implications for establishing a typology of participants based on quantitative criteria.
\end{abstract}

@@

In this paper we analyze the evolution of human interaction networks.
\hl{Directed and weighted representations were built through the observation of replies as links.}
Interaction networks from email lists were the most convenient for deriving results and for benchmarking while networks from Facebook, Twitter and Participabr were used for the sake of generalization.
Using a timeline of activity snapshots with a constant number of contiguous messages, we found remarkable stability (or invariance) for important network properties. For instance, activity along different timescales follows specific patterns; the most basic topological metrics can always be combined into characteristic principal components; and the fractions of participants in different sectors do not vary with time. This is not an intuitive result, given that participants constantly transition in network structure. Because these properties were shared by networks from various sources, and are consistent with the literature in complex networks~\cite{newmanBook}, we advocate that the conclusions might be valid for general classes of interaction networks. In particular, this allows us to 
bridge the gap between data analysis and social sciences in the discussion of types of networks and of participants.
It is worth noting that typologies are the canon of scientific literature for the classification of human agents, with pragmatic standards~\cite{myers} and critical paradigms~\cite{adorno,typCanon}.

@@

\hl{These two paragraphs were switched.}

@@

\begin{table}
\centering
\caption{Columns $date_1$ and $date_M$ have dates of first and last messages from the 20,000 messages considered in each email list.
$N$ is the number of participants (number of different email addresses),
$\Gamma$ is the number of discussion threads (count of messages without antecedent),
$\overline{M}$ is the number of messages missing in the 20,000 collection
($100\frac{23}{20000}=0.115$ percent in the worst case).
}
\label{tab:genLists}
\begin{tabular}{|l|c|c|c|c|c|}\hline
list & $date_1$ & $date_{M}$    & $N$  & $\Gamma$ & $\overline{M}$ \\\hline
\input{tables/tab1Overview}
\end{tabular}
\end{table}

\hl{"Availability" subsection heading removed}
The data and scripts used to derive the results, figures and tables, and this article itself are publicly available. Email messages are downloadable from the Gmane public database~\cite{Gmanewikipedia}.
Data annotated from Facebook and Twitter are in a public repository~\cite{fbtwData}.
Data from Participabr were used from the linked data/semantic web RDF triples~\cite{opa}, available in~\cite{datahub}.
Computer scripts are delivered through a public domain Python PyPI package and an open Git repository~\cite{gmanePack}.
This open approach to both data and scripts reinforces the scientific aspect of the contribution~\cite{openSci} and mitigates ethical and moral issues involved in researching systems constituted of human individuals~\cite{anPhy,ccs15}.
